%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage{fontawesome}



\name{Junsoo Ha}
\address{15-16, Majo-ro, Seongdong-gu \\ Seoul, Korea}
\address{\href{https://github.com/kuc2477}{\faGithub \hspace{0pt} kuc2477} \\ \href{https://www.linkedin.com/in/junsoo-ha-769a89bb/}{\faLinkedin \hspace{0pt} kuc2477} \\ \faEnvelope \hspace{0pt} junsoo.ha@vision.snu.ac.kr}

\begin{document}
	
	
%----------------------------------------------------------------------------------------
%	RESEARCH INTERESTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Interests}
	Theoretical foundation of multi-agent learning \\
	Intersection of game theory and machine learning
\end{rSection}
	

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf \href{https://www.snu.ac.kr/index.html}{Seoul National University}} \hfill{\em Seoul, Korea} \\
Master's student \hfill {\em Sep. 2020 - Present} \\ 
\href{https://gsai.snu.ac.kr/}{Graduate School of Artificial Intelligence} \\
Advisor: \href{https://vision.snu.ac.kr/gunhee/}{Prof. Gunhee Kim}


{\bf \href{https://www.hanyang.ac.kr/}{Hanyang University}} \hfill{\em Seoul, Korea} \\
Bachelor of Science in \href{http://cs.hanyang.ac.kr/}{Software} \hfill {\em Mar. 2013 - Aug. 2020} \\ 
Bachelor of Science in \href{http://math.hanyang.ac.kr}{Mathematics}\hfill{\em GPA: 4.08 / 4.5}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PUBLICATIONS}
	{\bf \href{https://openreview.net/forum?id=SJxSOJStPr}{A Neural Dicihlet Process Mixture Model for Task-Free Continual Learning}} \\ 
	Soochan Lee, {\bf Junsoo Ha}, Dongsu Zhang, Gunhee Kim \\
	{\em International Conference on Learning Representations (ICLR), 2020}
	
	
	{\bf \href{https://openreview.net/forum?id=HJxyAjRcFX}{Harmonizing Maximum Likelihood with GANs for Multimodal Conditional Generation}} \\ 
	Soochan Lee, {\bf Junsoo Ha}, Gunhee Kim \\
	{\em International Conference on Learning Representations (ICLR), 2019}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research \& Industrial Experience}

{\bf \href{https://vision.snu.ac.kr/}{SNU Vision \& Learning Lab.}} \hfill{\em Seoul, Korea} \\
\textit{Research Assistant} \hfill{\em Nov. 2017 - Present}

{\bf \href{https://www.buzzni.com/}{Buzzni}}\hfill{\em Seoul, Korea} \\
\textit{Backend Software Engineer} \hfill{\em Mar. 2017 - Jul. 2017}

{\bf Geopia}\hfill{\em Seoul, Korea}\\
\textit{Full-Stack Software Developer} \hfill{\em Apr. 2015 - Feb. 2017}

{\bf Nexol System}\hfill{\em Seoul, Korea}\\
\textit{Software Development Intern} \hfill{\em Jan. 2015 - Mar. 2015}

{\bf \href{https://www.lg.com/us}{LG Electronics}}\hfill{\em Seoul, Korea}\\
\textit{Software Development Intern} \hfill{\em Jul. 2014 - Aug. 2014}

\end{rSection}

%----------------------------------------------------------------------------------------
%	HONORS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Honors \& Awards}
	{\bf Samsung Human-Tech Paper Award} \hfill{2019}\\
	\textit{Samsung Electronics}\\
	2nd place; Silver Prize
	
	{\bf Distinguished Service Award} \hfill{2019}\\
	\textit{Hanyang University}
\end{rSection}

\newpage

%----------------------------------------------------------------------------------------
%	RELEVENT COURSEWORKS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Relevant Courseworks}
	{\bf Graduate} Optimization Theory and Applications\\
	{\bf Undergraduate}
	Artificial Intelligence, Deep Learning, Mathematical Statistics I-II, Abstract Algebra I-II, Topology I-II, Linear Algebra II, Ordinary Differential Equations, Advanced Calculus I, Vector Calculus, Differential Geometry, Non-Euclidean Geometry
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
	
	\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
		Machine Learning & PyTorch, Tensorflow \\
		Python & Django, Flask, SQLAlchemy, Celery \\
		JavaScript & ES6/7, React, Redux, Electron, Immutable \\
		Database & MySQL, PostgreSQL, SQLite, Redis
	\end{tabular}
	
\end{rSection}

\end{document}
